Carbonate chemistry at Ny-Ålesund

### 2022-08-03 awipev-CO2.Rmd
ranges are now fine with gtsummary

```{r Range per month, echo = FALSE, warning = FALSE}
# my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
#                                    med = ~ median(., na.rm = TRUE),
#                                    min = ~ min(., na.rm = TRUE),
#                                    max = ~ max(., na.rm = TRUE),
#                                    q5 = ~ quantile(., 0.05, na.rm = TRUE),
#                                    q95 = ~ quantile(., 0.95, na.rm = TRUE)
#                                    ), 
#                      append = FALSE)
# 
# range_month <-
#   d_all %>%
#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
#   group_by(montht) %>%
#   summarise(across(everything(), list(min=min, max=max), na.rm=TRUE))
# print(range_month)
# 
# range_month <-
#   d_all %>%
#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
#     group_by(montht) %>%
#   summary()
# print(range_month)

range_month <-
  d_all %>%
  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
tbl_summary(by = montht,
            missing = "no",
            type = all_continuous() ~ "continuous2",
            statistic = all_continuous() ~ c(
              "{mean}",
              "{median}",
              "{p25}",
              "{p75}",
              "{min}",
              "{max}"),
            digits = list(all_continuous() ~ c(2, 1, 1, 3)))
range_month

# range_month <-
#   d_all %>%
#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
#   group_by(montht) %>%
#   my_skim()
# print(range_month, include_summary = FALSE, width = 100)
```

>>>>

```{r Range per month, echo = FALSE, warning = FALSE}
range_month <-
  d_all %>%
  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
tbl_summary(by = montht,
            missing = "no",
            type = all_continuous() ~ "continuous2",
            statistic = all_continuous() ~ c(
              "{mean}",
              "{median}",
              "{p25}",
              "{p75}",
              "{min}",
              "{max}"),
            digits = list(sal_fb_mix ~ 1, temp_insitu_11m_mix ~ 1, temp_insitu_11m ~ 1, pHint_tot_sf_10m ~ 3))
range_month
```
